---
title: "Semantic inaccessibility and interference: eye-tracking models. Follow up experiment and combined data"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

This document presents summaries from eye-tracking experiments described in the paper: "Semantic accessibility and interference in pronoun resolution". First section contains summaries for the experiment 4 ("Follow-up experiment"). Second section contains Bayes factor summaries and pooled data analysis ("Combined analysis of eye-tracking experiments").

```{r cod1, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}

here::i_am("doc/models_summary.Rmd")

library(here)
library(tibble)
library(knitr)
library(dplyr)
library(purrr)
library(readr)
library(fs)

source(here("src/04-models_summary.R"))
source(here("src/03-models.R"))

dfs <- list.files(here("results"), pattern = "region[0-9].csv") %>%
  map(~ read_csv(here("results", .)))

opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE, error = FALSE,
  results = "asis", fig.path = here("figs/"), cache = TRUE
)
options(digits = 5)
## "[a-z]+_(full)|(split)_[a-z_86]+.csv"
res <- dir_ls(here("results"), regexp = "[a-z]{2,}_((split)|(full))") %>%
  map_dfr(read_csv, .id = "source") %>%
  mutate(source = path_file(source))
```

# Experiment 4: Follow-up eye-tracking experiment with only non-referential condition

Contrasts:
```{r contrasts-table }
dfs[[1]] %>%
  group_by(subj_cond, obj_cond) %>%
  summarise(
    subj_contrast = first(su),
    obj_contrast = first(ob)
  ) %>%
  mutate(
    "subj x obj" = subj_contrast * obj_contrast,
    subj_cond = if_else(subj_cond == "M",
      "match", "mis"
    ),
    obj_cond = if_else(obj_cond == "M",
      "match", "mis"
    ),
    "condition (subj, obj)" = paste(subj_cond, obj_cond,
      sep = ", "
    )
  ) %>%
  relocate("condition (subj, obj)") %>%
  ungroup() %>%
  select(-c(subj_cond:obj_cond)) %>%
  rename(
    subject = subj_contrast,
    object = obj_contrast
  ) %>%
  ## this is to generate the latex table
  ## select(starts_with("condition"):object) %>%
  ## kable(format = "latex")
  kable()
```

## Total fixation duration

Total fixations, all regions.

```{r tot }
res %>%
  filter(source == "totfixdur_full_models.csv") %>%
  select(-source) %>%
  kable()
```

```{r pps1, results = "markup" }
post_plots("totfixdur", dfs, .re = "totfixdur_r[5-8].rds")
post_plots("totfixdur", dfs, make_plot_func = pp_check, .re = "totfixdur_r[5-8].rds")
```


## Re-reading duration

Data was excluded when the subj did not re-read the region.

```{r rrdur }
res %>%
  filter(source == "rrdur_full_models.csv") %>%
  select(-source) %>%
  kable()
```

```{r pps_rrdur, results = "markup" }
post_plots("rrdur", dfs)
post_plots("rrdur", dfs, make_plot_func = pp_check)
```


## First pass regression path

Also called `rpdur`.

```{r rpdur }
res %>%
  filter(source == "rpdur_full_models.csv") %>%
  select(-source) %>%
  kable()
```

```{r pps_rpdur, results = "markup" }
post_plots("rpdur", dfs)
post_plots("rpdur", dfs, make_plot_func = pp_check)
```

## First pass


First pass first gaze, `gdur`. 

```{r gdur }
res %>%
  filter(source == "gdur_full_models.csv") %>%
  select(-source) %>%
  kable()
```

```{r pps_gdur, results = "markup" }
post_plots("gdur", dfs)
post_plots("gdur", dfs, make_plot_func = pp_check)
```


## Right bounded

Aka first pass total gaze, `tgdur`. 

```{r tgdur }
res %>%
  filter(source == "tgdur_full_models.csv") %>%
  select(-source) %>%
  kable()
```

```{r pps_tgdur, results = "markup" }
post_plots("tgdur", dfs, .re = "tgdur_r[5-8].rds")
post_plots("tgdur", dfs, make_plot_func = pp_check, .re = "tgdur_r[5-8].rds")
```

## Regressions

Probability of regression, `abs(gbck - 2)`. Bernoulli likelihood with logistic link, results on the logistic scale.

```{r gbck }
res %>%
  filter(source == "gbck_full_models.csv") %>%
  select(-source) %>%
  kable()
```

```{r pps_gbck, results = "markup" }
post_plots("gbck", dfs)
post_plots("gbck", dfs, make_plot_func = pp_check)
```



## Re-readings

`rr`. probability of re-reading  
Bernoulli likelihood with logistic link, results on the logistic scale.

```{r rr }
res %>%
  filter(source == "rr_full_models.csv") %>%
  select(-source) %>%
  kable()
```

```{r pps_rr, results = "markup" }
post_plots("rr", dfs, .re = "rr_r[5-8].rds")
post_plots("rr", dfs, make_plot_func = pp_check, .re = "rr_r[5-8].rds")
```

# Combined analysis of eye-tracking experiments

This section presents the result of the models fit to the data combined from the two experiments, and bayes factor analysis of these data.
The Bayes factor is always 10 i.e. the ratio of alternative to the null.

## Pooled data

Models fit to the data combined from the both experiments (without subsetting on subject condition).

```{r results-pooled }

dir_ls(here("models"), regexp = "comb") %>%
  map(readRDS) %>%
  msummary() %>%
  mutate(region = path_ext_remove(path_file(region))) %>%
  group_by(region) %>%
  mutate(
    measure = sub("comb_([a-z]+)_r([0-9]{1})", "\\1", region),
    region = as.numeric(sub("comb_([a-z]+)_r([0-9]{1})", "\\2", region))
  ) %>%
  ungroup() %>%
  relocate(measure) %>%
  kable()
```

```{r plots-pooled, results = "markup"}
post_plots("comb", NULL, .return = "available")
post_plots("comb", NULL, make_plot_func = pp_check, .return = "available")
```



## Subject mis-match

Models fit to the data combined from the both experiments, subset of the data where subject mismatched.
Numbers in the headers specify the parameters for the prior distribution on the slope of the object condition, used to fit the models and compute bayes factor.
This was a Normal distribution. For example mu = 0, sigma = 1 means that the prior was Normal(0, 1).

### mu = 0, sigma = 1

This is a bit silly, sigma this wide gives extreme support for the null.
Summaries of the posterior distribution:

```{r bf_helpers }

rename_summary <- function(dataf) {
  dataf %>%
    mutate(region = path_ext_remove(path_file(region))) %>%
    group_by(region) %>%
    mutate(
      measure = sub("bf_(totfixdur|tgdur)subj.*", "\\1", region),
      region = as.numeric(sub("bf_.*?([0-9]{1}).*", "\\1", region))
    ) %>%
    ungroup() %>%
    relocate(measure)
}

## debug = TRUE will print the models above the result table
bf_models_sum <- function(re, debug = FALSE) {
  if (debug == TRUE) {
    files <- dir_ls(here("models"), regexp = re) %>%
      path_file() %>%
      path_ext_remove()

    cat(paste0("    ", files, collapse = "\n"))
  }

  dir_ls(here("models"), regexp = re) %>%
    map(readRDS) %>%
    msummary() %>%
    rename_summary() %>%
    kable()
}


bf_table <- function(.subj, .mu, .sigma) {
  read_csv(here("results/bayes_factor.csv")) %>%
    filter(subj_cond == .subj, mu == .mu, sigma == .sigma) %>%
    group_by(dv_name, region) %>%
    summarise("mean bf_10" = mean(bf_10), sd = sd(bf_10)) %>%
    kable()
}
```

```{r bf_model1}
bf_models_sum("bf_.*subj_mis.*m0sd1")
```


Bayes factor (mean of 5 runs):
```{r bftable1}
bf_table("MIS", 0, 1)
```

### mu = 0, sigma = 0.1

```{r bfmodel3 }
bf_models_sum("bf_.*subj_mis.*m0sd0\\.1")
```

Bayes factor (mean of 5 runs):

```{r bftable3}
bf_table("MIS", 0, 0.1)
```

### mu = 0, sigma = 0.03

```{r bfmodel2 }
bf_models_sum("bf_.*subj_mis.*m0sd0\\.03")
```

Bayes factor (mean of 5 runs):

```{r bftable_}
bf_table("MIS", 0, 0.03)
```


### mu = -0.03, sigma = 0.009

These are the priors determined taken from the metaanalysis (Jager et al 2017).
The mean effect in the metaanalysis is -22 ms. This is assuming (+1/-1) contrast coding:


1. The key to the cabinet are in the kitchen. (-1, no interference)
2. The key to the cabinets are in the kitchen. (+1, "cabinets" interferes)

This matches what we have in these conditions:

1. MM_MM (MisMatch_MisMatch) De professor heeft geen zoon. De laatste paar jaar werkte zij helaas op alle feestdagen. (-1, no interference)
2. MM_M (MisMatch_Match) De professor heeft geen dochter. De laatste paar jaar werkte zij helaas op alle feestdagen. (+1, "dochter" interferes)

<!-- end of list -->

```{r bfmodel4 }
bf_models_sum("bf_.*subj_mis.*m-0\\.03sd0\\.009")
```

Bayes factor (mean of 5 runs):
```{r bftable}
bf_table("MIS", .mu = -0.03, .sigma = 0.009)
```

### mu -0.027, sigma = 0.009


```{r bfmodel5 }
bf_models_sum("bf_.*subj_mis.*m-0\\.027sd0\\.009")
```

Bayes factor (mean of 5 runs):
```{r bftable5}
bf_table("MIS", .mu = -0.027, .sigma = 0.009)
```

## Subject match

Models fit to the data combined from the both experiments, subset of the data where subject matched.
Numbers in the headers specify the parameters for the prior distribution on the slope of the object condition, used to fit the models and compute bayes factor.
This was a Normal distribution. For example mu = 0, sigma = 1 means that the prior was Normal(0, 1).

### mu = 0, sigma = 1

This is a bit silly, sigma this wide gives extreme support for the null.
Summaries of the posterior distribution:

```{r bf_model_ma_1 }
bf_models_sum("bf_.*subj_match.*m0sd1")
```

Bayes factor (mean of 5 runs):

```{r bftable_ma_1}
bf_table("MATCH", .mu = 0, .sigma = 1)
```

### mu = 0, sigma = 0.1

```{r bfmodel_ma_3 }
bf_models_sum("bf_.*subj_match.*m0sd0\\.1")
```

Bayes factor (mean of 5 runs):

```{r bftable_ma_3}

bf_table("MATCH", .mu = 0, .sigma = 0.1)
```

### mu = 0, sigma = 0.03

```{r bfmodel_ma_2 }

bf_models_sum("bf_.*subj_match.*m0sd0\\.03")
```

Bayes factor (mean of 5 runs):

```{r bftable_ma_}

bf_table("MATCH", .mu = 0, .sigma = 0.03)
```


### mu = -0.03, sigma = 0.009

For explanation see subject mis-match. Note that for subject match the contrasts are opposite.

```{r bfmodel_ma_4 }

bf_models_sum("bf_.*subj_match.*m-0\\.03sd0\\.009")
```

Bayes factor (mean of 5 runs):

```{r bftable_ma_4}

bf_table("MATCH", .mu = -0.03, .sigma = 0.009)
```

### mu = -0.027, sigma = 0.009


```{r bfmodel_ma_5 }

bf_models_sum("bf_.*subj_match.*m-0\\.027sd0\\.009")
```

Bayes factor (mean of 5 runs):

```{r bftable_ma_5}

bf_table("MATCH", .mu = -0.027, .sigma = 0.009)
```
